---
title: "Wednesday Night Basketball Stats"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ggplot2)
library(DT)
library(dplyr)
library(tidyr)
# devtools::install_github("haozhu233/kableExtra")
library(kableExtra)
library(lubridate)
source("ind_pg_funcs.R")
source("team_pg_funcs.R")
```
<head>
<!-- Global site tag (gtag.js) - Google Analytics -->
<script async src="https://www.googletagmanager.com/gtag/js?id=UA-151254232-1"></script>
<script>
  window.dataLayer = window.dataLayer || [];
  function gtag(){dataLayer.push(arguments);}
  gtag('js', new Date());
  gtag('config', 'UA-151254232-1');
</script>
</head> 
```{r data, include=FALSE, echo=FALSE}
df <- read.csv("data/individual_scores.csv", stringsAsFactors = FALSE)
df <- df[!is.na(df$Game) & df$Game!="", ]
tmsc <- read.csv("data/team_scores.csv", stringsAsFactors = FALSE)
games_w_pts <- get_games_w_pts(df)
tm_rec <- get_team_rec(tmsc)
```

*Site updated on `r Sys.time()`&nbsp;&nbsp;&nbsp;&nbsp; Data updated on `r file.mtime("data/individual_scores.csv")`*  
Official 2019-2020 WNB Schedule and Rules [word doc](https://drive.google.com/open?id=0Bz0dMuGXr7v5Nnc3YjNXT01UcElHX2VCVmtVZkJ0d0FUSXdZ)    
  
# Teams {.tabset .tabset-fade}   
```{r teamlist, echo=FALSE, results='asis'}
teamdf <- data.frame(`Team 1` = c("Jon D.", "Lance J.", "Ryan B.", "Brett J.",
                                  "Scott S.", "Mike B.", "Eric V.", "Mike W."),
                     `Team 2` = c("Mark S.", "Jay L.", "Ryan J.", "Chris L.", 
                                  "Brian H.", "Danny S.", "Chris T.", "Pat C."),
                     `Team 3` = c("Cory N.", "Pat B.", "Mike P.", "Mike S.",
                                  "John R.", "Alex P.", "Eric P.", "Steve F."),
                     `Team 4` = c("Frankie C.", "Jon T.", "Jordan F.", "Aaron M.",
                                  "Drew E.", "Jason W.", "Andy W.", "Marcelo D."),
                     stringsAsFactors = FALSE)
t1 <- kable(teamdf, align = 'c') %>%
  kable_styling(full_width = FALSE,
                bootstrap_options = c("striped", "condensed")) 
t2 <- kable(tm_rec, align = 'c') %>%
  kable_styling(full_width = FALSE,
                bootstrap_options = c("striped", "condensed")) 
cat(c('<table><tr valign="top"><td>', t1, '</td>', '<td>', 
      "&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;", 
      '</td>', '<td>', t2, '</td></tr></table>'),
    sep = '')
```

## Team 1 {.tabset .tabset-fade} 
### Team Stats 
```{r team1_sched, echo=FALSE}
tm1_results <- get_team_results(tmsc, 1)
kable(tm1_results[, names(tm1_results) != "color"], align = 'c', escape = FALSE) %>%
  kable_styling(full_width = FALSE,
                bootstrap_options = c("condensed")) %>% 
  row_spec(which(tm1_results$color == "#C8E9C2"), background = "#C8E9C2") %>%
  row_spec(which(tm1_results$color == "#E9C2C2"), background = "#E9C2C2")
```
### Individual Stats 
#### Points
```{r team1_pts, echo=FALSE, warning = FALSE, message = FALSE}
tm1_pts <- get_pts_df(df, 1)
kable(tm1_pts, linesep = "", align = 'c', row.names = FALSE) %>%
  kable_styling(full_width = TRUE,
                bootstrap_options = c("condensed")) %>%
   # row_spec(which(row.names(tm1_pts[tm1_pts$Date %in%
   #                               unique(tm1_pts$Date)[c(TRUE, FALSE)],])),
   #          background = "#f8f8f8") %>%

  row_spec(which(rownames(tm1_pts) %in% rownames(tm1_pts[tm1_pts$Date %in% unique(tm1_pts$Date)[c(TRUE, FALSE) == TRUE], ])),
            background = "#f8f8f8") %>%
  scroll_box(width = "100%", height = "500px")
```
#### Buckets
```{r team1_bkts, echo=FALSE, warning = FALSE, message = FALSE}
tm1_bkts <- get_bkts_df(df, 1)
kable(tm1_bkts, linesep = "", align = 'c', row.names = FALSE) %>%
  kable_styling(full_width = TRUE,
                bootstrap_options = c("condensed")) %>%
  row_spec(which(row.names(tm1_bkts) %in% row.names(tm1_bkts[tm1_bkts$Date %in%
                                unique(tm1_bkts$Date)[c(TRUE, FALSE)],])),
           background = "#f8f8f8") %>%
  scroll_box(width = "100%", height = "500px")
```
## Team 2 {.tabset .tabset-fade} 
### Team Stats 
```{r team2_sched, echo=FALSE}
tm2_results <- get_team_results(tmsc, 2)
kable(tm2_results[, names(tm2_results) != "color"], align = 'c', escape = FALSE) %>%
  kable_styling(full_width = FALSE,
                bootstrap_options = c("condensed")) %>% 
  row_spec(which(tm2_results$color == "#C8E9C2"), background = "#C8E9C2") %>%
  row_spec(which(tm2_results$color == "#E9C2C2"), background = "#E9C2C2")
```
### Individual Stats 
#### Points
```{r team2_pts, echo=FALSE, warning = FALSE, message = FALSE}
tm2_pts <- get_pts_df(df, 2)
kable(tm2_pts, linesep = "", align = 'c', row.names = FALSE) %>%
  kable_styling(full_width = TRUE,
                bootstrap_options = c("condensed")) %>%
  row_spec(which(row.names(tm2_pts) %in% row.names(tm2_pts[tm2_pts$Date %in%
                                unique(tm2_pts$Date)[c(TRUE, FALSE)],])),
           background = "#f8f8f8") %>%
  scroll_box(width = "100%", height = "500px")
```
#### Buckets
```{r team2_bkts, echo=FALSE, warning = FALSE, message = FALSE}
tm2_bkts <- get_bkts_df(df, 2)
kable(tm2_bkts, linesep = "", align = 'c', row.names = FALSE) %>%
  kable_styling(full_width = TRUE,
                bootstrap_options = c("condensed")) %>%
  row_spec(which(row.names(tm2_bkts) %in% row.names(tm2_bkts[tm2_bkts$Date %in%
                                unique(tm2_bkts$Date)[c(TRUE, FALSE)],])),
           background = "#f8f8f8") %>%
  scroll_box(width = "100%", height = "500px")
```
## Team 3 {.tabset .tabset-fade} 
### Team Stats  
```{r team3_sched, echo=FALSE}
tm3_results <- get_team_results(tmsc, 3)
kable(tm3_results[, names(tm3_results) != "color"], align = 'c', escape = FALSE) %>%
  kable_styling(full_width = FALSE,
                bootstrap_options = c("condensed")) %>% 
  row_spec(which(tm3_results$color == "#C8E9C2"), background = "#C8E9C2") %>%
  row_spec(which(tm3_results$color == "#E9C2C2"), background = "#E9C2C2")
```
### Individual Stats 
#### Points
```{r team3_pts, echo=FALSE, warning = FALSE, message = FALSE}
tm3_pts <- get_pts_df(df, 3)
kable(tm3_pts, linesep = "", align = 'c', row.names = FALSE) %>%
  kable_styling(full_width = TRUE,
                bootstrap_options = c("condensed")) %>%
  row_spec(which(row.names(tm3_pts) %in% row.names(tm3_pts[tm3_pts$Date %in%
                                unique(tm3_pts$Date)[c(TRUE, FALSE)],])),
           background = "#f8f8f8") %>%
  scroll_box(width = "100%", height = "500px")
```
#### Buckets
```{r team3_bkts, echo=FALSE, warning = FALSE, message = FALSE}
tm3_bkts <- get_bkts_df(df, 3)
kable(tm3_bkts, linesep = "", align = 'c', row.names = FALSE) %>%
  kable_styling(full_width = TRUE,
                bootstrap_options = c("condensed")) %>%
  row_spec(which(row.names(tm3_bkts) %in% row.names(tm3_bkts[tm3_bkts$Date %in%
                                unique(tm3_bkts$Date)[c(TRUE, FALSE)],])),
           background = "#f8f8f8") %>%
  scroll_box(width = "100%", height = "500px")
```
## Team 4 {.tabset .tabset-fade} 
### Team Stats  
```{r team4_sched, echo=FALSE}
tm4_results <- get_team_results(tmsc, 4)
kable(tm4_results[, names(tm4_results) != "color"], align = 'c', escape = FALSE) %>%
  kable_styling(full_width = FALSE,
                bootstrap_options = c("condensed")) %>% 
  row_spec(which(tm4_results$color == "#C8E9C2"), background = "#C8E9C2") %>%
  row_spec(which(tm4_results$color == "#E9C2C2"), background = "#E9C2C2")
```
### Individual Stats 
#### Points
```{r team4_pts, echo=FALSE, warning = FALSE, message = FALSE}
tm4_pts <- get_pts_df(df, 4)
kable(tm4_pts, linesep = "", align = 'c', row.names = FALSE) %>%
  kable_styling(full_width = TRUE,
                bootstrap_options = c("condensed")) %>%
  row_spec(which(row.names(tm4_pts) %in% row.names(tm4_pts[tm4_pts$Date %in%
                                unique(tm4_pts$Date)[c(TRUE, FALSE)],])),
           background = "#f8f8f8") %>%
  scroll_box(width = "100%", height = "500px")
```
#### Buckets
```{r team4_bkts, echo=FALSE, warning = FALSE, message = FALSE}
tm4_bkts <- get_bkts_df(df, 4)
kable(tm4_bkts, linesep = "", align = 'c', row.names = FALSE) %>%
  kable_styling(full_width = TRUE,
                bootstrap_options = c("condensed")) %>%
  row_spec(which(row.names(tm4_bkts) %in% row.names(tm4_bkts[tm4_bkts$Date %in%
                                unique(tm4_bkts$Date)[c(TRUE, FALSE)],])),
           background = "#f8f8f8") %>%
  scroll_box(width = "100%", height = "500px")
```




 



