---
title: "Wednesday Night Basketball Stats"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ggplot2)
library(DT)
library(dplyr)
```

```{r data, include=FALSE, echo=FALSE}
df <- read.csv("data/individual_scores.csv", stringsAsFactors = FALSE)
pl_agg <- df %>%
  group_by(Game, Player, Team) %>%
  summarize(`Total Points` = sum(Score),
            `Points (3s)` = sum(Score[Score == 3]),
            `Points (2s)` = sum(Score[Score == 2]),
            `Total Buckets` = length(Score),
            `Total 3s` = length(Score[Score == 3]),
            `Total 2s` = length(Score[Score == 2]))

get_transform <- function(df){
  tmp <- df %>%
    group_by(Player) %>%
    summarize(`Points (2s)` = sum(Score[Score == 2]),
              `Points (3s)` = sum(Score[Score == 3]),
              `Total Points` = sum(Score)) %>%
    t() %>%
    as.data.frame(stringsAsFactors = FALSE)
  #tmp <- data.frame(tmp)
  names(tmp) <- tmp[1,]
  tmp <- tmp[-1,]
  return(tmp)
}
#by_game_lists <- 
a <- df %>%  
  filter(Team == 3) %>%
    #get_transform(.)
  group_by(Game) %>%
  #do(get_transform(.))
  group_map(~ get_transform(.x))





            
```

## Teams
Team 1 | Team 2 | Team 3 | Team 4
------------- | ------------- | ------------- | -------------
Mike Brown | Tim Knight | Mike Wick | Mike Sroka
Pat Bodame | Rubin Jefferies | Frankie Cancino | Mike Perusky
Ryan Brown | Jon Turkowski | Andy White | Erik Villareal
Jason Workman | Steve Fisher | Adam Boness | Brian Falotico
Lance Johnson | Chris Truax | Danny Sackman | Matt Sroka
Howie Meyers | Brian Hawbaker | Joel Elfering | Jon Damon
Steve Gustafson | Jay Lerner | Cory Nissen | Ryan Christensen
Scott Stenzel | Pat Cook | Mike Silozis | Aaron Milks






 



